DATA 624 Project 1 Part B - Power

### 2020-03-21 DATA624/Project-1-B-Power.Rmd
More work on Project 1-B

---
title: "DATA 624 Project 1 Part B - Power"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
    toc_depth: 3
    code_folding: "hide"
---

```{r setup, echo=FALSE, cache=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = T, comment = NA, message = F, warning = F)
library(tidyverse)
library(readxl)
library(lubridate)
library(kableExtra)
library(fpp2)
library(forcats)
library(gridExtra)
options(scipen = 999)
```

@@

```{r}
raw_data <- read_excel("ResidentialCustomerForecastLoad-624.xlsx")
kwh <- raw_data %>%
  select(KWH) %>%
  ts(start = decimal_date(date("1998-01-01")), frequency = 12)

@@

```{r}
get_rmse <- function(e) {
  sqrt(mean(e^2, na.rm=TRUE))
}

arima_forecast <- function(x, h){forecast(Arima(x, order = c(3, 0, 1), seasonal = c(2, 1, 0), include.drift = TRUE), h = h)}

@@

data.frame(Model = c("ARIMA", "Holt-Winters", "Adjusted Holt-Winters", "Damped & Adjusted Holt-Winters"),
           RMSE = c(get_rmse(arima_errors[,h]), get_rmse(hw_error[,h]), get_rmse(adj_hw_error[,h]), get_rmse(damped_adj_hw_error[,h]))) %>%
  arrange(RMSE) %>%
  kable() %>%
  kable_styling()
```

@@

```{r}
my_forecast <- forecast(arima_fit, h = h)
autoplot(my_forecast)
  ggtitle("Forecasted Residential Power Consumption (KWH)") +
  theme(axis.title = element_blank())

@@

```{r}
data.frame(my_forecast$mean) %>%
  rename(KWH = my_forecast.mean)
```

>>>>

---
title: "DATA 624 Project 1 Part B - Power"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
    toc_depth: 3
    code_folding: "show"
---

```{r setup, echo=FALSE, cache=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = T, comment = NA, message = F, warning = F)
library(tidyverse)
library(readxl)
library(lubridate)
library(kableExtra)
library(fpp2)
library(forcats)
library(gridExtra)
library(openxlsx)
options(scipen = 999)
```

@@

```{r}
if (!file.exists("ResidentialCustomerForecastLoad-624.xlsx")) {
  download.file("https://github.com/mikeasilva/CUNY-SPS/raw/master/DATA624/ResidentialCustomerForecastLoad-624.xlsx", "ResidentialCustomerForecastLoad-624.xlsx")
}
raw_data <- read_excel("ResidentialCustomerForecastLoad-624.xlsx")
kwh <- raw_data %>%
  select(KWH) %>%
  ts(start = decimal_date(date("1998-01-01")), frequency = 12)

@@

```{r}
get_rmse <- function(e) {
  sqrt(mean(e^2, na.rm = TRUE))
}

arima_forecast <- function(x, h) {
  forecast(Arima(x, order = c(3, 0, 1), seasonal = c(2, 1, 0), include.drift = TRUE), h = h)
}

@@

data.frame(Model = c("ARIMA", "Holt-Winters", "Adjusted Holt-Winters", "Damped & Adjusted Holt-Winters"),
           RMSE = c(get_rmse(arima_errors[, h]), get_rmse(hw_error[, h]), get_rmse(adj_hw_error[, h]), get_rmse(damped_adj_hw_error[, h]))) %>%
  arrange(RMSE) %>%
  kable() %>%
  kable_styling()
```

@@

```{r}
my_forecast <- forecast(arima_fit, h = h)
autoplot(my_forecast) +
  ggtitle("Forecasted Residential Power Consumption (KWH)") +
  theme(axis.title = element_blank())

@@

```{r}
max_case_sequence <- max(raw_data$CaseSequence)
projections <- data.frame(my_forecast$mean) %>%
  rename(KWH = my_forecast.mean) %>%
  mutate(CaseSequence = row_number()) %>%
  rowwise() %>%
  mutate(`YYYY-MMM` = format(ymd(paste0("2014", ifelse(CaseSequence < 10, paste0("0", CaseSequence), CaseSequence), "01")), "%Y-%b")) %>%
  mutate(CaseSequence = CaseSequence + max_case_sequence) %>%
  ungroup() %>%
  select(CaseSequence, `YYYY-MMM`, KWH) %>%
  write.xlsx("2014ResidentialCustomerForecastLoad.xlsx")
```
